Code for Graphs for ASN presentation

### 2021-03-15 ASNCodeUpdatedFigs.Rmd
Got first graph working, after new data manipulation

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
library(viridisLite)
```

@@

data$outcome <- gsub(" mongo", "", data$outcome)
data$outcome <- gsub("em", "we", data$outcome)

@@

## Graphs

>>>>

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
library(viridisLite)
library(Rmisc)
```

@@

#data$outcome <- gsub(" mongo", "", data$outcome)
data$outcome <- gsub("em", "we", data$outcome)

@@

## Get means for data

```{r}
datalong <- data %>%
  select(ID, food, fate, mass.max, ttmax, area)

meantime <- summarySE(datalong, measurevar = "ttmax", groupvars = c("food", "fate"), na.rm = TRUE)

meanmass <- summarySE(datalong, measurevar = "mass.max", groupvars = c("food", "fate"), na.rm = TRUE)

meanarea <- summarySE(datalong, measurevar = "area", groupvars = c("food", "fate"), na.rm = TRUE)
```

### Group them into one dataframe

```{r}
datameans <- meantime %>%
  select(food, fate, ttmax, se)

datameans$mass.max <- meanmass$mass.max
datameans$semass <- meanmass$se
datameans$area <- meanarea$area
datameans$searea <- meanarea$se

## Graphs with means only

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = fate), 
       data = datameans) + 
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) +
  geom_point(size = 3) + 
  scale_shape_manual(values = c(5, 2, 1, 19)) + 
  geom_errorbar(aes(ymin = mass.max - semass, ymax = mass.max + semass), size = .5) + 
  geom_errorbarh(aes(xmin = ttmax - se, xmax = ttmax + se), size = .5) + 
  guides(size = FALSE) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Developmental Outcome", color = "Hostplant Consumed")
```

## Graphs with all datapoints
